---
title: "Titanic survival prediction"
format: html
embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(caret)
```

```{r}
df <- read.csv("train.csv")
df <- drop_na(df, Age)
df$Survived <- factor(df$Survived)
df$Sex <- factor(df$Sex)
df$Pclass <- factor(df$Pclass)
```

```{r}
summary(df)
```

Comparing survival rate of different classes
```{r}
#plot(df$Survived, as.numeric(df$Pclass))
```
There is a significantly larger number of Class 3 individuals who did not survive compared to those who survived.
```{r}
plot(df$Survived, df$Sex)
```
There is even larger difference between male and female passengers. Males were more probably to not survive.
```{r}
plot(df$Survived, df$Age)
```
For age, there is not a significant visible difference between those who survived, and those who do not. But we will run a test to compare two means.

We run a t test, to compare means.
```{r}

survived_index <- which(df$Survived==1)

test <- t.test(df$Age[survived_index], df$Age[-survived_index])
test$p.value
```
p value of ttest equals `r test$p.value`, so we reject null hypothesis that there is no statistical significant difference between age for survived, and not.

Mean age of not survived ones is aroud 30, which is smaller that survivals (28).





## todo model
```{r}
#| echo: false

df <- read.csv("train.csv")
df$Survived <- factor(df$Survived)
df$Sex <- factor(df$Sex)
df$Pclass <- factor(df$Pclass)

index <- createDataPartition(df$Survived, p = 0.7, list = FALSE)
train_data <- df[index, ]
test_data <- df[-index, ]

glm.fits <- glm(
  Survived ~ Sex + Pclass+Age, 
  family = binomial,
  data=train_data
)

summary(glm.fits)
probs <- predict(glm.fits, newdata = test_data, type = "response")
pred <- rep(0, length(probs))
pred[probs > .5] <- 1

table(pred, test_data$Survived)
```

```{r}
#| echo: false
head(train_data)

glm1 <- glm(Survived~Pclass+Sex+Age,family='binomial',data = train_data)
glm1 %>% summary()


```



