---
title: "BigBasket Products analysis"
author: "Patryk Tokarski"
date: '2022-07-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev = "CairoPNG"
)
knitr::opts_chunk$set(dev='CairoPNG')
```

### Loading database
```{r}
library(tidyverse)

# loading database without index and desc column
df <- read.csv("BigBasket Products.csv") %>% select(-index,-description)

# factor distinct columns
df <- df %>% mutate(category=as_factor(category),
              sub_category=as_factor(sub_category),
              brand=as_factor(brand),
              type=as_factor(type))
# adding discount column
df <- df %>% mutate(discount=round((market_price-sale_price)/market_price, digits = 3))
```
### Summary the data
```{r}
summary(df)
```
### % of NA's in rating category
```{r}
df %>% summarise(perc_of_na_rating = sum(is.na(rating))/n()*100)
```
#### About 31% of rating data don't have value.

### Data structure
```{r}
str(df)
```

### The most popular rating is about 4.
```{r}
df %>% ggplot(aes(x=rating, fill=..x..))+
  geom_histogram(show.legend = F)+
  scale_fill_gradient(low="red", high="green")
```

### What is the share of each category

```{r}
df %>% 
  group_by(category) %>% 
  summarise(count=n()) %>% 
  mutate(perc=count/sum(count)) %>% 
  arrange(count)%>% 
  ggplot(aes(y=fct_reorder(category, count), x=perc*100, fill=category))+
  geom_col(show.legend = F)+
  labs(x="Percent", y="", title = "Percentage of a category")+
  theme_minimal()
```

#### About 30% items are from Beauty category.


### Which brands have the best rating?
```{r}
df2 <- df %>% group_by(brand) %>% 
  filter(!is.na(rating)) %>% 
  summarise(mean_rating = mean(rating), n_element = n()) %>% 
  arrange(desc(mean_rating))
# top rating brands which have more than 4 products
df2 %>% filter(n_element>4) %>% head(10) %>% select(-n_element)
```

```{r}
# top rating brands which have more than 9 products
df2 %>% filter(n_element>9) %>% head(10) %>% select(-n_element)
```
### Discounts for each category?
```{r}
df %>% ggplot(aes(y=category, x=discount, color=category)) +
  geom_boxplot(show.legend=F)
```

#### The vast majority of discounts are from 0 to 20%.

#### We can see that there are suspiciously many values around 0.2  in the Fruits & Vegetables category.
```{r}
df %>% filter(category=="Fruits & Vegetables") %>% 
  summarise(discout_equal_0.2 =sum(discount==0.2)/n())
```

#### 87% of products from the Fruits & Vegetables category have 20% discount.


### Does discounting affect product rating?
```{r}

df %>% na.omit(rating) %>% 
ggplot(aes(discount, rating))+
geom_point()+
geom_smooth()+
facet_wrap(vars(category))

```

#### There is huge spread and it seems that discounting doesn't affect rating. For each category rating is about 4.
